### 2022-05-06 supplement.Rmd
trim-and-fill for frequentist

>>>>

```{r, trim_and_fill}

# random-effects 2 level model
r_mod <- rma.uni(yi = dat$gi, vi = dat$vi)

# run trim and fill
res_tf <- trimfill(r_mod)
print(res_tf)
res_string <- "The publication-bias-corrected effect size of mental rotation was 0.16"

summ_brm <- list(intercept = res_tf$beta)
# Compute funnel
funnel_z_crit <- stats::qnorm(0.975)
funnel_max_se <- 0.5 # A bit larger than the largest observed `sei` in `dat`
funnel_tau2 <- 0 # We don't take heterogeneity into account, only the SE
funnel <- data.frame(
  x = c(
    summ_brm$intercept - funnel_z_crit * sqrt(funnel_max_se^2 + funnel_tau2),
    summ_brm$intercept - funnel_z_crit * sqrt(funnel_tau2),
    summ_brm$intercept + funnel_z_crit * sqrt(funnel_tau2),
    summ_brm$intercept + funnel_z_crit * sqrt(funnel_max_se^2 + funnel_tau2)
  ),
  y = c(funnel_max_se, 0, 0, funnel_max_se)
)

# # Create funnel plot
plotdata <- as.data.frame(list(yi = res_tf$yi, vi = sqrt(res_tf$vi)))
ggplot(plotdata, aes(x = yi, y = sqrt(vi))) +
  geom_vline(xintercept = seq(-2, 2, 0.5), color = "grey90") +
  # Meta-analytic effect size
  geom_vline(xintercept = summ_brm$intercept, color = "black") +
  # Experiment-specific effect sizes
  geom_point(shape = 0) +
  # Funnel
  geom_path(data = funnel, aes(x = x, y = y), linetype = "dashed") +
  # Styling
  scale_x_continuous(breaks = seq(-2, 2, 0.5)) +
  scale_y_reverse() +
  coord_cartesian(
    xlim = c(-2.5, 2.5),
    ylim = c(funnel_max_se, 0),
    expand = FALSE
  ) +
  labs(
    x = expression("Hedges'" ~ italic("g")),
    y = "Standard error",
  ) +
  theme_classic() +
  theme(
    axis.line = element_line(colour = "black"),
    axis.text = element_text(family = "Helvetica", color = "black"),
    axis.ticks = element_line(color = "black"),
    text = element_text(family = "Helvetica", color = "black")
  )

# Save the plot
ggsave(here(figures_dir, "funnel_taf.pdf"), width = 5.56, height = 3.5)
```
